Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2021-05-14 minimax.tex
fit in 15 pages

@@

Note that in \cref{claim:rankPMR}, in the case $(x \pprefeq_j y)$, $\beta$ is the number of alternatives incomparable with both $x$ and $y$.
\begin{proposition}\label{claim:PMR}
	The $\PMR$ can be written as:
	\begin{align} 
		\PMR(x,y; \pprofile, W)  
		& = \max_{w \in W} \sum_{j \in N} w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)} = \max_{w \in W} \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_i 
	\end{align}
	where $\hat{\alpha}_{r}^{y}$ (resp. $\hat{\alpha}_{r}^{x}$)  is the number of times $y$ (resp. $x$) has rank $r$ in the complete profile $\hat{\profile}$ defined in \cref{claim:rankPMR}. 
\end{proposition}
%\cref{claim:rankPMR} can be understood by observing that in the case $(x \pprefeq_j y)$, $\beta$ is the number of alternatives incomparable with both $x$ and $y$.
\cref{claim:PMR}  shows that PMR is linear in the weights.
%Recall that $\pw$ represents the weight vectors compatible with the preferences of the chair stated so far.
The pairwise max regret $\PMR(x,y; \pprofile,W)$ can thus be obtained by solving the following linear program defined on the variables $w_1, …, w_m$:
\begin{align}
	\max_{\w} & \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_{r}\\
	\text{ s.t. } & w_1 = 1 ≥ … ≥ w_m = 0, \text{\cref{eq:convexity}} \text{ and } \w \in \pw.
\end{align}
%Note that given our choice $w_{1}=1$ and $w_{m}=0$, there are only $m-2$ variables 
%(we leave $w_{1}$ and $w_{m}$ in the LP just for clarity of presentation).
The max regret $\MaxR(x; \pprofile, W)$ is determined by computing the pairwise regret of $x$ with all other alternatives in $A$, and the recommended alternatives are the ones with least max regret. 
Observe that when the $\PMR$ of an alternative $x$ (against some other alternative $y$) exceeds the best MR value found so far, we do not need to further evaluate $x$. 
This idea can be exploited using a minimax-search tree \cite{Braziunas2012}.

@@

\begin{example*}
	Suppose we want to ask the following question to the chair: $w_{2} - w_{3} ≥ 2 (w_{3} - w_{4})$. We show the profile in Figure \ref{fig:profileQstComm} to the chair and ask who should win (each column is a preference of an agent).	Both $a$ and $b$ have scores higher than $c$ and $d$ for all convex weights, thus either $a$ or $b$ will be picked under our hypothesis; and $s(a) ≥ s(b) ⇔ w_2 + 2 w_4 ≥ 3 w_3$.
	Figure \ref{fig:profileQstCommCompact} shows the same profile using a compressed view, the numbers in bold indicating the number of agents having the preference in the corresponding column. As the proof shows, constructed profiles require only four different linear orders.
	\begin{figure}
		\centering
		\begin{subfigure}[b]{0.49\textwidth}
			\begin{center}
				$
				\begin{array}{ccccccccc}
					c&d&d&a&a&a&b&b&b\\
					a&c&c&b&b&b&a&a&a\\
					b&b&b&c&c&c&d&d&d\\
					d&a&a&d&d&d&c&c&c\\
				\end{array}.
				$
			\end{center}
			\caption{}
			\label{fig:profileQstComm}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.49\textwidth}
			\begin{center}
				$
				\begin{array}{cccc}
					\mathbf{1}&\mathbf{2}&\mathbf{3}&\mathbf{3} \\
					c&d&a&b\\
					a&c&b&a\\
					b&b&c&d\\
					d&a&d&c\\
				\end{array}.
				$
			\end{center}
			\caption{}
			\label{fig:profileQstCommCompact}
		\end{subfigure}
		\caption{Profile representing a question for the chair in extended (a) and compact (b) form.}
	\end{figure}
\end{example*}

@@

The oracle is built as follows. 
For the real preferences, we used three datasets from \href{https://www.preflib.org/}{PrefLib} \cite{PrefLib}: \textit{T Shirt} (researchers voted on tee shirt designs; $m \!=\! 11, n \!=\! 30$),
\textit{Courses}  (students voted on courses; $m \!=\! 9, n \!=\! 146$; referred to as AGH on PrefLib)
and \emph{Skate} (judges voted on skaters at the Euros Pairs Short Program; $m \!=\! 14, n \!=\! 9$).
% tee shirt designs voted by 
%$n \!=\! 30$ 
%members of the Optimization Research Group at NICTA;
% \textit{AGH Course Selection}: $m \!=\! 9$ courses evaluated by $n = 146$ students 
%of the AGH University; 
%and \emph{Skate}: $m \!=\! 14$ skaters evaluated by $n \!=\! 9$ judges at the Euros Pairs Short Program.
%We want to focus on the most critical setting, as there is a wide variety of possible situations to test in such experiments.
For the synthetic datasets, we follow an Impartial Culture (IC) assumption: the linear order of each agent is drawn i.i.d.\ uniformly.
%independently and all have the same probability of appearing. 
We believe IC to be a challenging situation and expect the number of questions to ask, in order to reach a certain level of regret, to decrease with less varied profiles.
%We adopt IC because it is a more challenging situation: as can be expected intuitively , the number of questions to be asked decrease with less varied profiles. 
To generate the scoring rule weights, we first draw $m \!-\! 1$ numbers uniformly at random (in the interval $\intvl{0,1}$ representing weight ``differences''), normalize and sort them; a sequence of convex decreasing weightx is then obtained by a decumulative sum. The penalty parameters for the Pessimistic and Extended pessimistic strategies are  $\epsilon_{\text{chair}} = 1.1$, $\epsilon'_{\text{chair}} = 10^{-6}$, $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.

\begin{figure}
	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
	\label{fig:smallSize}
	\begin{tikzpicture}
		\begin{axis}[
			y=8,
			xlabel=Number of Questions,
			ylabel=Avg. Regret,
			ytick={0,2,4,6,8,10},
			xtick distance=10,
			ytick distance=2,
			xtick pos=left,
			ymajorgrids=true,
			ytick style={draw=none},
			ymin=0,
			ymax=11,
			xmin=0,
			xmax=100,
			yticklabels={0,2,4,6,8,10},
			legend style={font=\scriptsize}]
			\addlegendimage{mark=*,teal,mark size=1.5}
			\addlegendimage{mark=triangle*,orange,mark size=1.5}
			\addlegendimage{mark=square*,blue,mark size=1.5}
			\addlegendimage{mark=diamond*,red,mark size=1.5}

@@

		\end{axis}
	\end{tikzpicture}
\end{figure}

%\begin{figure}
%	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
%	\label{fig:smallSize}
%%	\Description{Graph showing that Pessimistic performs slightly better than Extended pessimistic, itself performing better than Elitist, itself performing much better than Random.}
%	\includegraphics[width=.45\textwidth]{comparison.png}
%\end{figure}
\sisetup{table-number-alignment = center, table-figures-integer=2, table-figures-decimal=1, table-auto-round}
\begin{table}
	\caption{Average MMR in problems of size $(10, 20)$ after $k$ questions assuming geometric weights.}
	\label{tab:geometricWeights}
	\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]}
		\toprule
		{k} & {Pes.} & {sd} & {Eli.} & {sd} \\
		\midrule
		0	&20.0	&0.0	&20.0	&0.0\\
		50	&15.96	&0.54	&17.26	&0.42\\
		100	&12.48	&0.93	&15.6	&0.43\\
		150	&9.58	&1.37	&13.94	&0.76\\
		200	&7.43	&1.25	&10.95	&1.12\\
		250	&5.26	&1.52	&6.6	&0.79\\
		300	&3.47	&1.32	&6.57	&0.79\\
		\bottomrule
	\end{tabular}
\end{table}
\paragraph{Comparison of strategies}
Our first experiment concerns small size situations.
\Cref{fig:smallSize} compares some of our strategies in the case $m = 5, n = 10$ (variations around this size yield similar conclusions), where the results are averaged over $200$ runs.
%(The figure also displays the performance of the Elitist strategy, to which we will come back.)
We see that asking random questions does not allow to reach a low regret level even after having asked 100 questions, whereas a low regret level ($\MMR \!=\! 1$) is reached by Pessimistic before having asked 60 questions. This also holds for other problem sizes. For instance, for $m =10$, $n = 20$ and $400$ questions, Random strategy reaches an average regret (over 10 runs) of $12$ (±$ 0.7$) and Pessimistic $0.6$ (±$ 0.5$).
We notice that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since Pessimistic is much faster: it takes on average only $16$s for a complete elicitation session (for $m = 5$, $n = 10$ and $100$ questions), while Extended pessimistic takes $50$s. Although their performance is close, Pessimistic performs systematically better in multiple runs of the experiment.

@@

\paragraph{Evaluation of Pessimistic Strategy}
\label{sec:lowRegret}
Our next set of experiments evaluate the Pessimistic strategy in absolute terms. 
We first wonder how many questions should be asked in order to achieve low regret, fixed at $n / 10$: this is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where a tenth of the agents rank $x$ last instead of first. Another interesting measure is the average number of questions asked to each participant before reaching zero regret. The results for various sizes are displayed in \cref{tab:questions}. The notation $q_{c {\scriptscriptstyle \MMR}≤ x}$ indicates the number of questions asked to the committee to reach a threshold regret $x$, averaged on $20$ runs. We use a similar notation for the questions to the voters $q_{v {\scriptscriptstyle \MMR}≤ x}$, but in this case we display the quartiles ([Q1|M|Q3]) of the number of questions asked to the voters, averaged on $20$ runs. It is important to mention that we stop our computation at $1000$ questions, the empty cells in \cref{tab:questions} indicate, thus, that the Pessimistic strategy applied to that dataset did not reach zero regret in $1000$ questions.

%For example, in the case $m = 10, n = 20$, Pessimistic asks on average $49$ questions to the chair and $18$ questions to each agent (\cref{tab:Numquestions} provides more data).

\begin{table}[ht]
	\caption{Analysis of the questions asked by Pessimistic strategy on the datasets of \cref{fig:linearity}. The column $q_{c \scriptscriptstyle{\MMR} ≤ n/10}$ ($q_{c \scriptscriptstyle{\MMR} = 0}$) indicates the average number of questions asked to the chair to reach a threshold regret of $\frac{n}{10}$ (zero regret). The column $q_{v \scriptscriptstyle{\MMR} ≤ n/10}$ ($q_{v \scriptscriptstyle{\MMR} = 0}$) represents the average of the quartiles of the questions asked to the voters to reach $\frac{n}{10}$ regret (zero regret).}
	\label{tab:questions}
	\begin{tabular}{cccS[table-number-alignment = right, table-figures-integer=2]@{ ± }S[table-number-alignment = left, table-figures-integer=2] S[table-figures-integer=3, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ ]} S[table-number-alignment = right, table-figures-integer=2]@{ ± }S[table-number-alignment = left, table-figures-integer=2]S[table-figures-integer=3, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ ]}}
		\toprule
		{dataset} & m & n &{$q_{c \scriptscriptstyle{\MMR} ≤ n/10}$} & {sd} & \multicolumn{3}{c}{$q_{v \scriptscriptstyle{\MMR} ≤ n/10}$} & {$q_{c \scriptscriptstyle{\MMR} = n/10}$} & {sd} & \multicolumn{3}{c}{$q_{v \scriptscriptstyle{\MMR} = 0}$} \\
		\midrule
		m5n20 & 5&20&0.0&0.0&[4.3 &4.95 & 5.84 &5.25&9.59&[ \ 5.36 & 6.15 & 7.21\\
		m10n20&10&20&0.0&0.0&[13.85 & 16.1& 18.41&31.95&26.62&[19.66 & 21.78 & 24.7\\
		m11n30&11&30&0.0&0.0&[16.55&19.0&22.26&45.15&40.14&[23.07&25.7&28.89\\
		tshirts&11&30&0.0&0.0&[12.92 & 16.17 &19.3\\
		courses&9&146&0.0&0.0&[6.35 &7.0 &7.0&0.0&0.0&[6.8 & 7.0 &7.0\\
		%m9n146&9&146&0&0&[1.94 &8 &9.25&999.3&0.47&0&0&[1.94&8&9.25&999.3&0.47\\
		m14n9&14&9&5.4&9.49&[30.3&33.45&36.65&64.05&40.37&[37.55&40.5&44.3\\
		skate&14&9&0.0&0.0&[11.35&11.8&12.25&0.0&0.0&[11.5&11.9&12.7 \\
		m15n30&15&30&0.0&0.0&[24.95&29.5&33.68&\multicolumn{2}{c}{---}&\multicolumn{3}{c}{---} \\

@@

\begin{figure}
	\caption{Average MMR (normalized by $n$) after $k$ questions with Pessimistic strategy for different datasets.}
	\label{fig:linearity}
	\begin{tikzpicture}
		\pgfplotsset{
			every axis legend/.append style={
				at={(0.5,1.1)},
				anchor=south
			},
		}
		\begin{axis}[
			y=80,
			legend columns=3,
			xlabel=Number of Questions,
			ylabel=MMR/n,
			ytick={0,0.5,1},
			xtick distance=100,
			xtick pos=left,
			ymajorgrids=true,
			ytick style={draw=none},
			ymin=0,
			ymax=1,
			xmin=0,
			xmax=1000,
			yticklabels={0,0.5,1},
			legend style={font=\footnotesize}]

@@

			\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {120}, brown] table [x=k, y=5.20]{data/linearity_redone.dat};
			\addlegendentry{m=5, n=20}
			\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {150}, red] table [x=k, y=10.20]{data/linearity_redone.dat};
			\addlegendentry{m=10, n=20}
			\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {240}, cyan] table [x=k, y=11.30]{data/linearity_redone.dat};
			\addlegendentry{m=11, n=30}
			\addplot[thick, mark=halfcircle*, mark size = {2}, mark indices = {400}, violet] table [x=k, y=tshirts]{data/linearity_redone.dat};
			\addlegendentry{tshirts m11n30}
			\addplot[thick, mark=*, mark size = {2}, mark indices = {400}, pink] table [x=k, y=courses]{data/linearity_redone.dat};
			\addlegendentry{courses m9n146}
			\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {400}, green] table [x=k, y=9.146]{data/linearity_redone.dat};
			\addlegendentry{m=9, n=146}
			\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, blue] table [x=k, y=14.9]{data/linearity_redone.dat};
			\addlegendentry{m=14, n=9}
			\addplot[thick, mark=square*, mark size = {2}, mark indices = {60}, teal] table [x=k, y=skate]{data/linearity_redone.dat};
			\addlegendentry{skate m14n9}
			\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, magenta] table [x=k, y=15.30]{data/linearity_redone.dat};
			\addlegendentry{m=15, n=30}
		\end{axis}
	\end{tikzpicture}
\end{figure}

%\subsection{Value of information comparison}
\paragraph{Comparison with Two Phases}

%\begin{table}
%	\caption{Average MMR in problems of size $(10, 20)$ after $400$ questions, among which $q_c$ to the chair.}
%	\label{tab:twoP400}
%	\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]}
%		\toprule
%		{$q_c$} & {2 ph.\ ca} & {sd} & {2 ph.\ ac} & {sd} \\
%		\midrule
%		0 & 0.86 & 0.72 & 0.73 & 0.67 \\
%		15 & 0.92 & 0.82 & 0.93	& 0.96  \\
%		30 & 0.9 & 0.97 & 0.72	& 0.7 \\
%		50 & 1.36 & 1.29 & 1.38	& 1.17 \\
%		100 & 1.9 & 1.72 & 2.5	& 1.46  \\
%		%150 & 4.4 & 2.09 & 4.23 & 1.53 \\
%		200 & 6.05	& 1.53  & 6.06 & 1.61 \\
%		%250 & 8.27	& 1.54& 8.86 & 1.38 \\
%		300 &11.54	& 1.07& 11.82 &1.25 \\
%		%350 &15.39	& 0.61 &15.54	&0.73 \\
%		400 &20.0 & 0.0 & 20.0 & 0.0 \\
%		\bottomrule
%	\end{tabular}
%\end{table}

>>>>

%\renewcommand{\UrlFont}{\ttfamily\scriptsize}

@@

Note that in \cref{claim:rankPMR}, in the case $(x \pprefeq_j y)$, $\beta$ is the number of alternatives incomparable with both $x$ and $y$.
\begin{proposition}\label{claim:PMR}
	The $\PMR$ can be written as:
	\begin{align} 
		\PMR(x,y; \pprofile, W)  
		& = \max_{w \in W} \sum_{j \in N} w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)} = \max_{w \in W} \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_i 
	\end{align}
	where $\hat{\alpha}_{r}^{y}$ (resp. $\hat{\alpha}_{r}^{x}$)  is the number of times $y$ (resp. $x$) has rank $r$ in the complete profile $\hat{\profile}$ defined in \cref{claim:rankPMR}. 
\end{proposition}
%\cref{claim:rankPMR} can be understood by observing that in the case $(x \pprefeq_j y)$, $\beta$ is the number of alternatives incomparable with both $x$ and $y$.
\cref{claim:PMR}  shows that PMR is linear in the weights.
%Recall that $\pw$ represents the weight vectors compatible with the preferences of the chair stated so far.
The pairwise max regret $\PMR(x,y; \pprofile,W)$ can thus be obtained by solving the following linear program defined on the variables $w_1, …, w_m$:
\begin{align}
	\max_{\w} \sum_{r=1}^m (\hat{\alpha}_{r}^{y} - \hat{\alpha}_{r}^{x}) w_{r} \quad
	\text{ s.t. } w_1 = 1 ≥ … ≥ w_m = 0, \text{\cref{eq:convexity}} \text{ and } \w \in \pw.
\end{align}
%Note that given our choice $w_{1}=1$ and $w_{m}=0$, there are only $m-2$ variables 
%(we leave $w_{1}$ and $w_{m}$ in the LP just for clarity of presentation).
The max regret $\MaxR(x; \pprofile, W)$ is determined by computing the pairwise regret of $x$ with all other alternatives in $A$, and the recommended alternatives are the ones with least max regret. 
Observe that when the $\PMR$ of an alternative $x$ (against some other alternative $y$) exceeds the best MR value found so far, we do not need to further evaluate $x$. 
This idea can be exploited using a minimax-search tree \cite{Braziunas2012}.

@@

\begin{example*}
	Suppose we want to ask the following question to the chair: $w_{2} - w_{3} ≥ 2 (w_{3} - w_{4})$. We show the profile in Figure \ref{fig:profileQstComm} to the chair and ask who should win (each column is a preference of an agent).	Both $a$ and $b$ have scores higher than $c$ and $d$ for all convex weights, thus either $a$ or $b$ will be picked under our hypothesis; and $s(a) ≥ s(b) ⇔ w_2 + 2 w_4 ≥ 3 w_3$.
	Figure \ref{fig:profileQstCommCompact} represents the same profile using a compressed view, the numbers in bold indicating the number of agents having the preference in the corresponding column. As the proof shows, constructed profiles require only four different linear orders.
	\begin{figure}
		\centering
		\begin{subfigure}[b]{0.49\textwidth}
			\begin{center}
				$
				\begin{array}{ccccccccc}
					c&d&d&a&a&a&b&b&b\\
					a&c&c&b&b&b&a&a&a\\
					b&b&b&c&c&c&d&d&d\\
					d&a&a&d&d&d&c&c&c\\
				\end{array}.
				$
			\end{center}
			\caption{}
			\label{fig:profileQstComm}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.49\textwidth}
			\begin{center}
				$
				\begin{array}{cccc}
					\mathbf{1}&\mathbf{2}&\mathbf{3}&\mathbf{3} \\
					c&d&a&b\\
					a&c&b&a\\
					b&b&c&d\\
					d&a&d&c\\
				\end{array}.
				$
			\end{center}
			\caption{}
			\label{fig:profileQstCommCompact}
		\end{subfigure}
		\caption{Profile representing a question to the chair in extended (a) and compact (b) form.}
	\end{figure}
\end{example*}

@@

The oracle is built as follows. 
For the real preferences, we used three datasets from \href{https://www.preflib.org/}{PrefLib} \cite{PrefLib}: \textit{T Shirt} (researchers voted on tee shirt designs; $m \!=\! 11, n \!=\! 30$),
\textit{Courses}  (students voted on courses; $m \!=\! 9, n \!=\! 146$; referred to as AGH on PrefLib)
and \emph{Skate} (judges voted on skaters at the Euros Pairs Short Program; $m \!=\! 14, n \!=\! 9$).
% tee shirt designs voted by 
%$n \!=\! 30$ 
%members of the Optimization Research Group at NICTA;
% \textit{AGH Course Selection}: $m \!=\! 9$ courses evaluated by $n = 146$ students 
%of the AGH University; 
%and \emph{Skate}: $m \!=\! 14$ skaters evaluated by $n \!=\! 9$ judges at the Euros Pairs Short Program.
%We want to focus on the most critical setting, as there is a wide variety of possible situations to test in such experiments.
For the synthetic datasets, we follow an Impartial Culture (IC) assumption: the linear order of each agent is drawn i.i.d.\ uniformly.
%independently and all have the same probability of appearing. 
We believe IC to be a challenging situation and expect the number of questions to ask, in order to reach a certain level of regret, to decrease with less varied profiles.
%We adopt IC because it is a more challenging situation: as can be expected intuitively , the number of questions to be asked decrease with less varied profiles. 
To generate the scoring rule weights, we first draw $m \!-\! 1$ numbers uniformly at random (in the interval $\intvl{0,1}$ representing weight ``differences''), normalize and sort them; a sequence of convex decreasing weights is then obtained by a decumulative sum. The penalty parameters for the Pessimistic and Extended pessimistic strategies are  $\epsilon_{\text{chair}} = 1.1$, $\epsilon'_{\text{chair}} = 10^{-6}$, $\epsilon_{\text{agent}} = 1.0$ and $\epsilon'_{\text{agent}} = 0$.
\sisetup{table-number-alignment = center, table-figures-integer=2, table-figures-decimal=1, table-auto-round}
\begin{minipage}{\textwidth}
	\vspace{0.4cm}
	\begin{minipage}{\textwidth}
		\centering
		\captionof{figure}{Average MMR in problems of size $(5, 10)$ after $k$ questions.}
		\label{fig:smallSize}
		\scalebox{0.85}{
		\begin{tikzpicture}
			\begin{axis}[
				y=8,
				xlabel=Number of Questions,
				ylabel=Avg. Regret,
				ytick={0,2,4,6,8,10},
				xtick distance=10,
				ytick distance=2,
				xtick pos=left,
				ymajorgrids=true,
				ytick style={draw=none},
				ymin=0,
				ymax=11,
				xmin=0,
				xmax=100,
				yticklabels={0,2,4,6,8,10},
				legend style={font=\scriptsize}]
				\addlegendimage{mark=*,teal,mark size=1.5}
				\addlegendimage{mark=triangle*,orange,mark size=1.5}
				\addlegendimage{mark=square*,blue,mark size=1.5}
				\addlegendimage{mark=diamond*,red,mark size=1.5}

@@

			\end{axis}
		\end{tikzpicture}
		}
	\end{minipage}
	\vspace{0.2cm}

	\begin{minipage}{\textwidth}
		\centering
		\captionof{table}{Average MMR in problems of size $(10, 20)$ after $k$ questions assuming geometric weights.}
		\label{tab:geometricWeights}
		\scalebox{0.85}{
		\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]}
			\toprule
			{k} & {Pes.} & {sd} & {Eli.} & {sd} \\
			\midrule
			0	&20.0	&0.0	&20.0	&0.0\\
			50	&15.96	&0.54	&17.26	&0.42\\
			100	&12.48	&0.93	&15.6	&0.43\\
			150	&9.58	&1.37	&13.94	&0.76\\
			200	&7.43	&1.25	&10.95	&1.12\\
			250	&5.26	&1.52	&6.6	&0.79\\
			300	&3.47	&1.32	&6.57	&0.79\\
			\bottomrule
		\end{tabular}
		}
	\end{minipage}
	\vspace{0.4cm}
\end{minipage}

\paragraph{Comparison of strategies}
Our first experiment concerns small size situations.
\Cref{fig:smallSize} compares some of our strategies in the case $m = 5, n = 10$ (variations around this size yield similar conclusions), where the results are averaged over $200$ runs.
%(The figure also displays the performance of the Elitist strategy, to which we will come back.)
We see that asking random questions does not allow to reach a low regret level even after having asked 100 questions, whereas a low regret level ($\MMR \!=\! 1$) is reached by Pessimistic before having asked 60 questions. This also holds for other problem sizes. For instance, for $m =10$, $n = 20$ and $400$ questions, Random strategy reaches an average regret (over 10 runs) of $12$ (±$ 0.7$) and Pessimistic $0.6$ (±$ 0.5$).
We notice that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since Pessimistic is much faster: it takes on average only $16$s for a complete elicitation session (for $m = 5$, $n = 10$ and $100$ questions), while Extended pessimistic takes $50$s. Although their performance is close, Pessimistic performs systematically better in multiple runs of the experiment.

@@

\paragraph{Evaluation of Pessimistic Strategy}
\label{sec:lowRegret}
Our next set of experiments evaluate the Pessimistic strategy in absolute terms. 
We first wonder how many questions should be asked in order to achieve low regret, fixed at $n / 10$: this is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where a tenth of the agents rank $x$ last instead of first. Another interesting measure is the average number of questions asked to each participant before reaching zero regret. The results for various sizes are displayed in \cref{tab:questions}. The notation $q_{c {\scriptscriptstyle \MMR}≤ x}$ indicates the number of questions asked to the chair to reach a threshold regret $x$, averaged on $20$ runs. We use a similar notation for the questions to the voters $q_{v {\scriptscriptstyle \MMR}≤ x}$, but in this case we display the quartiles ([Q1|M|Q3]) of the number of questions asked to the voters, averaged on $20$ runs. It is important to mention that we stop our computation at $1000$ questions, the empty cells in \cref{tab:questions} indicate, thus, that the Pessimistic strategy applied to that dataset did not reach zero regret in $1000$ questions.
%For example, in the case $m = 10, n = 20$, Pessimistic asks on average $49$ questions to the chair and $18$ questions to each agent (\cref{tab:Numquestions} provides more data).
\vspace{-0.6cm}
\begin{table}
	\caption{Questions asked by Pessimistic strategy on several datasets. The column $q_{c \scriptscriptstyle{\MMR} ≤ n/10}$ ($q_{c \scriptscriptstyle{\MMR} = 0}$) indicates the avg number of questions asked to the chair to reach a threshold regret of $\frac{n}{10}$ (zero regret). The column $q_{v \scriptscriptstyle{\MMR} ≤ n/10}$ ($q_{v \scriptscriptstyle{\MMR} = 0}$) represents the avg of the quartiles of the questions asked to the voters to reach $\frac{n}{10}$ regret (zero regret).}
	\label{tab:questions}
	\begin{tabular}{cccS[table-number-alignment = right, table-figures-integer=2]@{ ± }S[table-number-alignment = left, table-figures-integer=2] S[table-figures-integer=3, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ ]} S[table-number-alignment = right, table-figures-integer=2]@{ ± }S[table-number-alignment = left, table-figures-integer=2]S[table-figures-integer=3, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ ]}}
		\toprule
		{dataset} & m & n &{$q_{c \scriptscriptstyle{\MMR} ≤ n/10}$} & {sd} & \multicolumn{3}{c}{$q_{v \scriptscriptstyle{\MMR} ≤ n/10}$} & {$q_{c \scriptscriptstyle{\MMR} = n/10}$} & {sd} & \multicolumn{3}{c}{$q_{v \scriptscriptstyle{\MMR} = 0}$} \\
		\midrule
		m5n20 & 5&20&0.0&0.0&[4.3 &4.95 & 5.84 &5.25&9.59&[ \ 5.36 & 6.15 & 7.21\\
		m10n20&10&20&0.0&0.0&[13.85 & 16.1& 18.41&31.95&26.62&[19.66 & 21.78 & 24.7\\
		m11n30&11&30&0.0&0.0&[16.55&19.0&22.26&45.15&40.14&[23.07&25.7&28.89\\
		tshirts&11&30&0.0&0.0&[12.92 & 16.17 &19.3\\
		courses&9&146&0.0&0.0&[6.35 &7.0 &7.0&0.0&0.0&[6.8 & 7.0 &7.0\\
		%m9n146&9&146&0&0&[1.94 &8 &9.25&999.3&0.47&0&0&[1.94&8&9.25&999.3&0.47\\
		m14n9&14&9&5.4&9.49&[30.3&33.45&36.65&64.05&40.37&[37.55&40.5&44.3\\
		skate&14&9&0.0&0.0&[11.35&11.8&12.25&0.0&0.0&[11.5&11.9&12.7 \\
		m15n30&15&30&0.0&0.0&[24.95&29.5&33.68&\multicolumn{2}{c}{---}&\multicolumn{3}{c}{---} \\

@@

\begin{minipage}{\textwidth}
	\vspace{0.4cm}
	\begin{minipage}{\textwidth}
		\centering
		\captionof{figure}{Average MMR (normalized by $n$) after $k$ questions with Pessimistic strategy for different datasets.}
		\label{fig:linearity}
		\begin{tikzpicture}
			\pgfplotsset{
				every axis legend/.append style={
					at={(0.5,1.1)},
					anchor=south
				},
			}
			\begin{axis}[
				y=80,
				legend columns=3,
				xlabel=Number of Questions,
				ylabel=MMR/n,
				ytick={0,0.5,1},
				xtick distance=100,
				xtick pos=left,
				ymajorgrids=true,
				ytick style={draw=none},
				ymin=0,
				ymax=1,
				xmin=0,
				xmax=1000,
				yticklabels={0,0.5,1},
				legend style={font=\footnotesize}]

@@

				\addplot[thick, mark=halfsquare right*, mark size = {2}, mark indices = {120}, brown] table [x=k, y=5.20]{data/linearity_redone.dat};
				\addlegendentry{m=5, n=20}
				\addplot[thick, mark=diamond*, mark size = {2}, mark indices = {150}, red] table [x=k, y=10.20]{data/linearity_redone.dat};
				\addlegendentry{m=10, n=20}
				\addplot[thick, mark=pentagon*, mark size = {2}, mark indices = {240}, cyan] table [x=k, y=11.30]{data/linearity_redone.dat};
				\addlegendentry{m=11, n=30}
				\addplot[thick, mark=halfcircle*, mark size = {2}, mark indices = {400}, violet] table [x=k, y=tshirts]{data/linearity_redone.dat};
				\addlegendentry{tshirts m11n30}
				\addplot[thick, mark=*, mark size = {2}, mark indices = {400}, pink] table [x=k, y=courses]{data/linearity_redone.dat};
				\addlegendentry{courses m9n146}
				\addplot[thick, mark=triangle*, mark size = {2}, mark indices = {400}, green] table [x=k, y=9.146]{data/linearity_redone.dat};
				\addlegendentry{m=9, n=146}
				\addplot[thick, mark=halfsquare left*, mark size = {2}, mark indices = {200}, blue] table [x=k, y=14.9]{data/linearity_redone.dat};
				\addlegendentry{m=14, n=9}
				\addplot[thick, mark=square*, mark size = {2}, mark indices = {60}, teal] table [x=k, y=skate]{data/linearity_redone.dat};
				\addlegendentry{skate m14n9}
				\addplot[thick, mark=halfsquare*, mark size = {2}, mark indices = {400}, magenta] table [x=k, y=15.30]{data/linearity_redone.dat};
				\addlegendentry{m=15, n=30}
			\end{axis}
		\end{tikzpicture}
	\end{minipage}
	\vspace{0.2cm}

	\begin{minipage}{\textwidth}
		\centering
		\captionof{table}{Average MMR in problems of size $(10, 20)$ after $500$ questions, among which $q_c$ to the chair.}
		\label{tab:twoP500}
		\scalebox{0.85}{
		\begin{tabular}{S[table-figures-integer=3, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left, table-figures-integer=1]}
			\toprule
			{$q_c$} & {2 ph.\ ca} & {sd} & {2 ph.\ ac} & {sd} \\
			\midrule		
			0	&0.78&	0.38&	0.78&	0.38\\
			15	&0.58&	0.3	&   0.63&   0.26\\
			30	&0.29&  0.31&	0.4&    0.52\\
			50	&0.0&	0.0&	0.0&	0.0\\
			100	&0.21&	0.36&	0.07&	0.12\\
			200	&2.84&	1.52&	1.72&	1.79\\
			300	&6.02&	2.28&	6.79&	0.81\\
			400	&10.95&	0.74&	12.8&	0.92\\
			500	&20.0&	0.0&	20.0&	0.0\\

			\bottomrule
		\end{tabular}
		}
	\end{minipage}
	\vspace{0.4cm}
\end{minipage}
%\subsection{Value of information comparison}
\paragraph{Comparison with Two Phases}
